\sysfull

### 2017-08-11 paper/coalescing.tex
coalescing figure revised

The key challenge to coalescing tasks is determining how many tasks to coalesce before committing. During execution, an executing task is either a {\em coalesced} task, which does not commit its state before transitioning or a {\em committing} task, which does commit its state before transitioning. \sys monitors a program's execution to adaptively determine $C$, the number of tasks to coalesce before committing; \sys repeatedly executes $C-1$ coalesced tasks, followed by a committing task.

@@

\noindent\textbf{Task Coalescing Illustration:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes eight tasks in the first operating period, assigning $C=4$. \sys completes only two of the four coalesced tasks in the next operating period and then power fails. \sys sets $C=(6+8+2)/2$ in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.\todo{Rewrite this paragraph to reflect what is in the figure}{Przemek}

>>>>

The challenge to coalescing tasks is determining how many tasks to coalesce before committing. During execution, an executing task is either a {\em coalesced} task, which does not commit its state before transitioning or a {\em committing} task, which does commit its state before transitioning. \sys monitors a program's execution to adaptively determine $C$, the number of tasks to coalesce before committing; \sys repeatedly executes $C-1$ coalesced tasks, followed by a committing task.

@@

\noindent\textbf{Task Coalescing Implementation:} Figure~\ref{fig:coalescing_example} illustrates how \sys coalesces tasks. Figure~\ref{fig:coalescing_example_states} (left) shows a sequence of three tasks executing in \sys with no coalescing, incurring the cost of commit at each task transition. The same figure shows the same sequence of tasks executing as coalesced groups of three tasks $C=2$ (center) and $C=3$ (right). Figure~\ref{fig:coalescing_example_flowchart} shows how \sys adapts the value of $C$ based on $S$. \sys executes eight tasks in the first operating period, assigning the half of previous $C=8/2$. \sys completes only two of the four coalesced tasks in the next operating period and then power fails. \sys sets $C=(6+8+2)/2$ in the next operating period, coalescing pairs of tasks and successfully committing two pairs before power fails. Execution resumes at the start of the third pair of tasks with a coalescing factor of two. If a larger number of tasks successfully complete in the next operating period, i.e., $S$ is larger, $C$ correspondingly increases, allowing more aggressive coalescing.\todo{Rewrite this paragraph to reflect what is in the figure}{Przemek}
